---
title: "Fractal Curvature"
author: "Peter Straka"
date: "02/01/2015"
output:
  html_document:
    keep_md: yes
---

This page illustrates calculations from the paper [Estimation of fractal dimension and fractal curvatures from digital images](http://arxiv.org/abs/1408.6333). 
After loading the workspace [fracCurv.RData](fracCurv.Rdata), the data sets for the six fractal sets (gasket, carpet, modcarpet, quadrate, triangle, supergasket) become available. 
These were calculated using the Java library [GeoStoch](http://www.uni-ulm.de/en/mawi/institute-of-stochastics/software.html); see [here](./?) for the main method. 
The images have resolution $3000 \times 3000$, or $1500 \times 1500$ if the number `2` appears in the data set name.


### Non-arithmetic fits

The method LRE (linear regression estimate) is called as follows: 

```{r, echo=TRUE, eval=FALSE}
fracCurv(gasket,arithmetic = FALSE)
```

This results in a linear fit to the data 
$y_{kj}  := \log \left( \varepsilon_j^{-k} |C_k(F_{\varepsilon_j})|\right), \quad k=0,\ldots, d$. The output contains estimated fractal dimension, curvatures and fitted linear model.

```{r LRE, echo=FALSE, eval=TRUE, fig.path="./figure/"}
fracCurv(gasket,arithmetic = FALSE)
```

### Arithmetic fits

Compare the above to the method NRE (nonlinear regression estimate): 

```{r, echo=TRUE, eval=FALSE}
fracCurv(gasket,arithmetic = TRUE)
```

Here the period is estimated via a periodogram of the data: 

```{r NRE, echo=FALSE, eval=TRUE, fig.path="./figure/"}
fracCurv(gasket,arithmetic = TRUE)
```


### Fits with known dimension

Assuming the dimension is known, a fit is performed e.g. as 

```{r, echo=TRUE, eval=FALSE}
fracCurv(gasket[,c(1,2)],arithmetic = FALSE, frac.dim = log(3)/log(2))
```

Note that only one characteristic can be fitted at a time, here for $k = 0$. 
If dimension and period are known (for _arithmetic_ fractals) one calls e.g.

```{r, echo=TRUE, eval=FALSE}
fracCurv(gasket[,c(1,2)],arithmetic = TRUE, frac.dim = log(3)/log(2), period = log(2))
```

